Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-24 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
2016 Kingaroy AUDPC entered and some other code improvements

unique(Herm_16$Treatment)
```

@@

Herm_16_dat <- 
   data.frame(trial_ref = "mung1516/01",
              year = "2016",
              location = "Hermitage",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = 12,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = Herm_16_dat$rep,
              planting_date = as.Date("2016-02-03", format = "%Y-%m-%d"),
              emergence_date = as.Date("2016-02-12", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date("2016-04-15", format = "%Y-%m-%d"),
              first_sign_disease = as.Date("2016-03-08", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_16_dat$trade_name),
              fungicide_ai = Herm_16_dat$fungicide_ai,
              dose_ai.ha = Herm_16_dat$dose_ai.ha,
              n_treatment = as.numeric(Herm_16_dat$Treatment),
              fungicide_application_1 = Herm_16_dat$fungicide_application_1,
              fungicide_application_2 = Herm_16_dat$fungicide_application_2,
              fungicide_application_3 = Herm_16_dat$fungicide_application_3,
              total_fungicide = Herm_16_dat$spray_n,
              harvest_date = as.Date("2015-05-06", format = "%Y-%m-%d"),
              final_assessment = as.Date("2015-04-15", format = "%Y-%m-%d"),
              PM_final_severity = NA,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Herm_16_dat$`Raw.Adjusted.Yeild./.ha`)
              )
```

@@

King_16_dat <- 
   data.frame(trial_ref = "mung1516/02",
              year = "2016",
              location = "Kingaroy",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = 12,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = King_16_dat$rep,
              planting_date = as.Date("2016-02-11", format = "%Y-%m-%d"),
              emergence_date = as.Date("2016-02-19", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date("2016-04-05", format = "%Y-%m-%d"),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2016-03-09", format = "%Y-%m-%d"),
              trade_name = as.factor(King_16_dat$trade_name),
              fungicide_ai = King_16_dat$fungicide_ai,
              dose_ai.ha = King_16_dat$dose_ai.ha,
              n_treatment = as.numeric(King_16_dat$Treatment),
              fungicide_application_1 = King_16_dat$fungicide_application_1,
              fungicide_application_2 = King_16_dat$fungicide_application_2,
              fungicide_application_3 = King_16_dat$fungicide_application_3,
              total_fungicide = King_16_dat$spray_n,
              harvest_date = as.Date("2016-05-10", format = "%Y-%m-%d"),
              final_assessment = as.Date("2016-04-19", format = "%Y-%m-%d"),
              PM_final_severity = NA,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(King_16_dat$`Raw.Adjusted.Yeild./.ha`)
              )
```

#### Calculating treatment means
```{r King16_means}
King_16_m <- King_16_dat %>%
   group_by(host_genotype, n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = unique(plant_density),
             row_spacing = unique(row_spacing),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             fungicide_application_3 = unique(fungicide_application_3),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             #PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             #disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             #D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = "Yes",
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             #AUDPC.m = mean(AUDPC),
             #AUDPC.sd = sd(AUDPC),
             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[1,3]
   )

@@

King_16_m <- left_join(King_16_m,King_16.DR)
King_16_m$AUDPC.m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
                            FUN = audpc, dates = c(1,14,26,40))

King_16_m <- fold_data(King_16_m, PM_MB_means)

@@

#### Define treatment data
```{r King16_treatmentDefine}
Fogerty_17_dat <- Fogerty_17 %>%
   mutate(trade_name = 
             case_when(Chem.Trt == 1 ~ "Folicur",
                       Chem.Trt == 2 ~ "Throttle",
                       Chem.Trt == 3 ~ "Custodia",
                       TRUE ~ "other"))%>%
   mutate(fungicide_ai = 
             case_when(Chem.Trt == 1 ~ "tebuconazole",
                       Chem.Trt == 2 ~ "propiconazole",
                       Chem.Trt == 3 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
                       TRUE ~ "other"))%>%
   mutate(dose_ai.ha = 
             case_when(Chem.Trt == 1 ~ 62,
                       Chem.Trt == 2 ~ 125,
                       Chem.Trt == 3 ~ 60,
                       TRUE ~ 9999))%>%
   mutate(fungicide_application_1 = 
             case_when(Treatment.No == 1 ~ as.Date(NA),
                       Treatment.No == 2 ~ as.Date("2017-02-22", format = "%Y-%m-%d"),
                       Treatment.No == 3 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
                       Treatment.No == 4 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
                       Treatment.No == 5 ~ as.Date("2017-03-19", format = "%Y-%m-%d"),
                       Treatment.No == 6 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_2 = 
             case_when(Treatment.No == 4 ~ as.Date("2017-03-24", format = "%Y-%m-%d"),
                       Treatment.No == 6 ~ as.Date("2017-04-02", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(spray_n = 
             case_when(Treatment == 1 ~ 0,
                       Treatment == 4 ~ 2,
                       Treatment == 6 ~ 2,
                       TRUE ~ 1))

@@

Fogerty_17_dat <- 
   data.frame(trial_ref = "mung1617/02",
              year = "2017",
              location = "Missen Flats",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = 10,
              plot_width = 2,
              plant_density = Fogerty_17_dat$`Population.plsnts/ha`,
              row_spacing = Fogerty_17_dat$`Row.Spacing.(m)`,
              replicate = Fogerty_17_dat$Rep,
              planting_date = as.Date("2017-01-27", format = "%Y-%m-%d"),
              emergence_date = as.Date("2017-02-01", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2017-03-07", format = "%Y-%m-%d"),
              trade_name = as.factor(Fogerty_17_dat$trade_name),
              fungicide_ai = Fogerty_17_dat$fungicide_ai,
              dose_ai.ha = Fogerty_17_dat$dose_ai.ha,
              n_treatment = as.numeric(Fogerty_17_dat$Treatment.No),
              fungicide_application_1 = Fogerty_17_dat$fungicide_application_1,
              fungicide_application_2 = Fogerty_17_dat$fungicide_application_2,
              total_fungicide = Fogerty_17_dat$spray_n,
              harvest_date = as.Date("2017-05-11", format = "%Y-%m-%d"),
              final_assessment = as.Date("2017-04-18", format = "%Y-%m-%d"),
              PM_final_severity = Fogerty_17_dat$`2017-04-18`,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Fogerty_17_dat$`Yield.t/ha`),
              AUDPC = apply(Fogerty_17_dat[,c("2017-03-07", "2017-03-19", "2017-03-24", "2017-04-02","2017-04-10","2017-04-18")]-1,1, 
                            FUN = audpc, dates = c(1,12,17,26,34,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              )
```

@@

Fogerty_17_m <- Fogerty_17_dat %>%
   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )

# For some weird reason standard deviations are comming back NA in the code above
Fogerty_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
   Fogerty_17_dat %>%
   group_by(n_treatment, row_spacing, fungicide_ai) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

@@

Herm_17_m <- Herm_17_dat %>%
   group_by(n_treatment, fungicide_ai,row_spacing) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
                                  factor(n_treatment) + fungicide_ai + row_spacing, 
                               data = subset(Herm_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )

>>>>

@@

Herm_16_dat <- 
   data.frame(trial_ref = "mung1516/01",
              year = "2016",
              location = "Hermitage",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = 12,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = Herm_16_dat$rep,
              planting_date = as.Date("2016-02-03", format = "%Y-%m-%d"),
              emergence_date = as.Date("2016-02-12", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date("2016-04-15", format = "%Y-%m-%d"),
              first_sign_disease = as.Date("2016-03-08", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_16_dat$trade_name),
              fungicide_ai = Herm_16_dat$fungicide_ai,
              dose_ai.ha = Herm_16_dat$dose_ai.ha,
              n_treatment = as.numeric(Herm_16_dat$Treatment),
              fungicide_application_1 = Herm_16_dat$fungicide_application_1,
              fungicide_application_2 = Herm_16_dat$fungicide_application_2,
              fungicide_application_3 = Herm_16_dat$fungicide_application_3,
              total_fungicide = Herm_16_dat$spray_n,
              harvest_date = as.Date("2015-05-06", format = "%Y-%m-%d"),
              final_assessment = as.Date("2015-04-15", format = "%Y-%m-%d"),
              PM_final_severity = NA,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Herm_16_dat$`Raw.Adjusted.Yeild./.ha`),
              stringsAsFactors = FALSE)
```

@@

King_16_dat <- 
   data.frame(trial_ref = "mung1516/02",
              year = "2016",
              location = "Kingaroy",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = 12,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = King_16_dat$rep,
              planting_date = as.Date("2016-02-11", format = "%Y-%m-%d"),
              emergence_date = as.Date("2016-02-19", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date("2016-04-05", format = "%Y-%m-%d"),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2016-03-09", format = "%Y-%m-%d"),
              trade_name = as.factor(King_16_dat$trade_name),
              fungicide_ai = King_16_dat$fungicide_ai,
              dose_ai.ha = King_16_dat$dose_ai.ha,
              n_treatment = as.numeric(King_16_dat$Treatment),
              fungicide_application_1 = King_16_dat$fungicide_application_1,
              fungicide_application_2 = King_16_dat$fungicide_application_2,
              fungicide_application_3 = King_16_dat$fungicide_application_3,
              total_fungicide = King_16_dat$spray_n,
              harvest_date = as.Date("2016-05-10", format = "%Y-%m-%d"),
              final_assessment = as.Date("2016-04-19", format = "%Y-%m-%d"),
              PM_final_severity = NA,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(King_16_dat$`Raw.Adjusted.Yeild./.ha`),
              stringsAsFactors = FALSE)
```

#### Calculating treatment means
```{r King16_means}
King_16_m <- King_16_dat %>%
   group_by(host_genotype, n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = unique(plant_density),
             row_spacing = unique(row_spacing),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             fungicide_application_3 = unique(fungicide_application_3),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             #PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             #disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             #D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = "Yes",
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             #AUDPC.m = mean(AUDPC),
             #AUDPC.sd = sd(AUDPC),
             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[1,3]
   )

@@

King_16_m <- left_join(King_16_m,King_16.DR)
King_16_m$AUDPC_m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
                            FUN = audpc, dates = c(20,34,46,60))
King_16_m$AUDPC_se <- NA

King_16_m <- fold_data(King_16_m, PM_MB_means)
King_16_m <- King_16_m[,!colnames(King_16_m) %in% c('Treatment',"dae20","dae34","dae46","Final_Yield_tHa", "AUDPC.m")]

@@

#### Define treatment data
```{r Fog17_treatmentDefine}
Fogerty_17_dat <- Fogerty_17 %>%
   mutate(trade_name = 
             case_when(Chem.Trt == 1 ~ "Folicur",
                       Chem.Trt == 2 ~ "Throttle",
                       Chem.Trt == 3 ~ "Custodia",
                       TRUE ~ "other"))%>%
   mutate(fungicide_ai = 
             as.character(case_when(Chem.Trt == 1 ~ "tebuconazole",
                                    Chem.Trt == 2 ~ "propiconazole",
                                    Chem.Trt == 3 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
                                    TRUE ~ "other")))%>%
   mutate(dose_ai.ha = 
             case_when(Chem.Trt == 1 ~ 62,
                       Chem.Trt == 2 ~ 125,
                       Chem.Trt == 3 ~ 60,
                       TRUE ~ 9999))%>%
   mutate(fungicide_application_1 = 
             case_when(Treatment.No == 1 ~ as.Date(NA),
                       Treatment.No == 2 ~ as.Date("2017-02-22", format = "%Y-%m-%d"),
                       Treatment.No == 3 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
                       Treatment.No == 4 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
                       Treatment.No == 5 ~ as.Date("2017-03-19", format = "%Y-%m-%d"),
                       Treatment.No == 6 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_2 = 
             case_when(Treatment.No == 4 ~ as.Date("2017-03-24", format = "%Y-%m-%d"),
                       Treatment.No == 6 ~ as.Date("2017-04-02", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(spray_n = 
             case_when(Treatment.No == 1 ~ 0,
                       Treatment.No == 4 ~ 2,
                       Treatment.No == 6 ~ 2,
                       TRUE ~ 1))

@@

Fogerty_17_dat <- 
   data.frame(trial_ref = "mung1617/02",
              year = "2017",
              location = "Missen Flats",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = 10,
              plot_width = 2,
              plant_density = Fogerty_17_dat$`Population.plsnts/ha`,
              row_spacing = Fogerty_17_dat$`Row.Spacing.(m)`,
              replicate = Fogerty_17_dat$Rep,
              planting_date = as.Date("2017-01-27", format = "%Y-%m-%d"),
              emergence_date = as.Date("2017-02-01", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2017-03-07", format = "%Y-%m-%d"),
              trade_name = as.factor(Fogerty_17_dat$trade_name),
              fungicide_ai = as.character(Fogerty_17_dat$fungicide_ai),
              dose_ai.ha = Fogerty_17_dat$dose_ai.ha,
              n_treatment = as.numeric(Fogerty_17_dat$Treatment.No),
              fungicide_application_1 = Fogerty_17_dat$fungicide_application_1,
              fungicide_application_2 = Fogerty_17_dat$fungicide_application_2,
              total_fungicide = Fogerty_17_dat$spray_n,
              harvest_date = as.Date("2017-05-11", format = "%Y-%m-%d"),
              final_assessment = as.Date("2017-04-18", format = "%Y-%m-%d"),
              PM_final_severity = Fogerty_17_dat$`2017-04-18`,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Fogerty_17_dat$`Yield.t/ha`),
              AUDPC = apply(Fogerty_17_dat[,c("2017-03-07", "2017-03-19", "2017-03-24", "2017-04-02","2017-04-10","2017-04-18")]-1,1, 
                            FUN = audpc, dates = c(1,12,17,26,34,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              , stringsAsFactors = FALSE)
```

@@

Fogerty_17_m <- Fogerty_17_dat %>%
   group_by(n_treatment, row_spacing, fungicide_ai) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             host_genotype = unique(host_genotype),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )

# For some weird reason standard deviations are comming back NA in the code above
Fogerty_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <-
   Fogerty_17_dat %>%
   group_by(n_treatment, row_spacing, fungicide_ai) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("n_treatment","row_spacing","disease_error","yield_error"))

Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "fungicide_ai"] <- "control"
Fogerty_17_m[Fogerty_17_m$n_treatment == 1,"dose_ai.ha"] <- NA_real_
Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "trade_name"] <- NA

@@

Herm_17_m <- Herm_17_dat %>%
   group_by(n_treatment, fungicide_ai,row_spacing) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             host_genotype = unique(host_genotype),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
                                  factor(n_treatment) + fungicide_ai + row_spacing, 
                               data = subset(Herm_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )
